\section{Motivation}
Spreadsheets are one of the most common computer tools, with an estimated user base exceeding one billion users~\cite{gislason_excel_2021}. This popularity is largely attributed to their accessibility. Users can store and organize their data almost instantly without writing traditional code. This allows for quick "what-if" projections of their data for decision-making, as noted in \textit{The first killer app: a history of spreadsheets}~\cite{zynda_first_2013}.
Although spreadsheets do not require traditional programming, users still write formulas which can create complex dependency chains, especially when working across multiple worksheets. This hidden complexity can manifest as "spreadsheet smells", which are structural weaknesses such as excessive cross-worksheet dependencies \cite{hermans_detecting_2012}, which can hinder comprehension and make it difficult for users to find relevant information.
These smells hinder comprehension and make it harder for the user to find the relevant information. Ragavan et al., in \textit{Spreadsheet Comprehension: Guesswork, Giving Up and Going Back to the Author}~\cite{srinivasa_ragavan_spreadsheet_2021}, find that readers of spreadsheet spend approximately 40\% of their time on information detours. This involves locating items, understanding interactions, tracing formula logic or understanding unfamiliar spreadsheet concepts. This shows that there exists a need for tools to help spreadsheet users navigate and understand the underlying complexity of spreadsheets.






%Spreadsheets are prone to weak points known as Spreadsheet smells. Common smells are Feature Envy, where a formula accumulates excessive dependencies, and Inappropriate Intimacy, where data is tightly coupled across different worksheets \cite{hermans_detecting_2012}. These smells hinder comprehension and make it harder for the users to find information. Readers of Spreadsheet spent 40\% of their time seeking for information, such as locating items, understanding interactions, tracing formula logic and understanding unfamiliar spreadsheet concepts \cite{srinivasa_ragavan_spreadsheet_2021}.
%Improving Self-descriptiveness is therefore critical to reduce the time spent seeking for information. However visualization alone is insufficient. The lack of Bidirectionality forces users to constantly switch context on these information detours, further increasing the time and cognitive effort required.