\section{Problem statement}
\label{sec:problem-statement}
The study conducted by Ragavan et al. suggests that information detouring contributes to approximately 40\% of the time needed to understand a spreadsheet. In some cases, participants even failed to obtain the relevant information. Information detouring involves identifying dependents of a cell, understanding the underlying logic of a certain value and understanding unfamiliar concepts. Another time-consuming task is formula tracing. This occurs when a formula refers to another cell address, which in turn refers to another, thereby creating a chain of dependencies. Although modern spreadsheet programs highlight referenced cells on the grid, it is not sufficient when the cells are not visible in the grid or located in a different worksheet~\cite{srinivasa_ragavan_spreadsheet_2021}. During this process, users are often forced to navigate away from their current position in the spreadsheet. This can lead to spatial context loss, where the users navigate back and forth between positions. Furthermore, when users discover a value or a logic error, existing tools require users to find and resolve these issues in the spreadsheet rather than directly in the tool itself. 
These challenges highlight a gap in the current spreadsheet programs. While there is a clear need to improve the visualization for the logic of a spreadsheet, visualization alone is not enough. To address the problem of information detours, a tool must actively support the user in the navigation process as well as allow direct manipulation within the tool, to make it easier to find relevant information while minimizing the loss of spatial context.



%comprehension process is the information detouring. Where the dependencies and logic of the related data is not directly visible to the user \cite{srinivasa_ragavan_spreadsheet_2021}.
%Another problem for comprehending a Spreadsheet is the lost context when going from author to reader. The author has more context on the provenance on the data of the Spreadsheet than the reader which implies that there is a lack of presenting the locality and relationship of the data \cite{kohlhase_context_nodate}. These problems indicate first that there is still a need for a tool to improve the presenting and visualizing of the underlying logic of a Spreadsheet. But visualizing alone is not enough. The tool also has to support the navigation process without hindering to build a mental model of the system.