\section{Cognitive dimensions}
To describe and evaluate certain design choices, this thesis uses vocabulary from the paper \textit{Usability Analysis of Visual Programming Environments: A 'Cognitive Dimensions' Framework} by Green and Petre~\cite{green_usability_1996}. The Cognitive Dimensions Framework has a small vocabulary in order to capture the important aspects of visual programming environments. The following dimensions are particularly relevant:

\begin{definition}
    \label{def:diffuseness}
    \textbf{Diffuseness} is defined as "How many symbols or graphic entities are required to express a meaning?" \cite[p.~138]{green_usability_1996}
\end{definition}
Diffuseness in this thesis is used to describe whether the flow-graph requires many nodes to represent the logic and therefore is not compact.

\begin{definition}
    \label{def:role-expressiveness}
    \textbf{Role expressiveness} is defined as "Can the reader see how each component of a program relates to the whole?" \cite[p.~139]{green_usability_1996}
\end{definition}
Role expressiveness is used to describe if the purpose of a certain component in the flow-graph can be inferred from its appearance and how it interacts with the other nodes. If the flow-graph has high role expressiveness, the user should be able to infer how the components relate to the underlying logic of the spreadsheet from only reading the flow-graph.

\begin{definition}
    \label{def:hidden-dependencies}
    \textbf{Hidden dependencies} are defined as "Is every dependency overtly indicated in both directions? Is the indication perceptual or only symbolic?" \cite[p.~139]{green_usability_1996}
\end{definition}
Green and Petre mention an example of hidden dependencies in spreadsheets: "The formula in a cell tells which other cells it takes its value from, but does not tell which other cells take their value from it." \cite[p.~154]{green_usability_1996}. This thesis evaluates whether the flow-graph is able to show these dependencies and make them visible.

\begin{definition}
    \label{def:viscosity}
    \textbf{Viscosity} is defined as "How much effort is required to perform a single change?" \cite[p.~139]{green_usability_1996}
\end{definition}
Viscosity is relevant to evaluating both the navigation cost of tracing dependencies and describing the ease of making changes in the edit mode.

\begin{definition}
    \label{def:closeness-of-mapping}
    \textbf{Closeness of mapping} is defined as "What programming games need to be learned?" \cite[p.~138]{green_usability_1996}
\end{definition}
In this thesis, closeness of mapping is used to describe whether interactions in the flow-graph correspond to interactions the user already knows from existing spreadsheet tools.

\begin{definition}
    \label{def:juxtaposability}
    \textbf{Juxtaposability} is defined as the ability to see any two portions of the program on screen side-by-side at the same time \cite[p.~162]{green_usability_1996}
\end{definition}
Juxtaposability is relevant to evaluating whether the user can view both the spreadsheet and the flow-graph simulataneously.