\begin{abstract}
    Spreadsheet programs are one of the most widely used computational tools. Previous research identified that existing spreadsheet tools offer limited support in the spreadsheet comprehension process. In particular, users spend a significant portion of their time on information detours. This thesis presents a flow-graph based visualization. The visualization aims to improve the self-descriptiveness of formulas by exposing their hidden dependency structures. Additionally, it supports users during the navigation process through interactive features and bidirectional editing, enabling users to modify formulas directly in the flow-graph. The visualization is displayed alongside the spreadsheet, preserving the user's spatial context while tracing dependencies across worksheets. To evaluate the usefulness, an explorative study was conducted with five participants, who had to solve three tasks and fill out the NASA-TLX, UEQ+ and answer three open-ended questions. The overall NASA-TLX mean was 27.7 out of 100 and the UEQ+ score indicates a positive experience among the participants. In the open-ended questions the participants confirmed that they found the tool helpful to understand formulas and intuitive to use for navigating. However, the study was explorative and did not include sessions where participants used only traditional spreadsheet tools. Therefore, to be able to correctly identify the benefits of the tool, future work should conduct a more extensive study.
\end{abstract}