\section{Study Discussion}
The low-to-moderate NASA-TLX scores suggest that the tool does not impose heavy cognitive demands, while the positive UEQ+ scores indicate a positive user experience across different dimensions. Taken together with the qualitative feedback from the custom questions, the three sources show a consistent result: the participants found the tool helpful for understanding formula logic and navigating dependencies, but they also revealed specific areas for future improvement.

The results suggest that the flow graph fulfills the core design goals. Participants confirmed that the tool helped them understand the logic behind cell values. This suggests that the tool is able to make hidden dependencies visible. The positive feedback about navigation suggests that the split-view approach reduces the viscosity of tracking dependencies. Despite encountering specific usability problems, the frustration ratings on the NASA-TLX remained low. This could suggest that even when participants encountered problems, the visualization still offered enough support to make progress. Several participants encountered confusion when attempting to directly edit formula output values in the flow graph, which the tool did not support. Yet, overall satisfaction remained positive, as reflected in the UEQ+ Usefulness score and the generally positive answers in the custom questions. However, this confusion likely contributed to the Dependability subscale receiving the lowest score (M=1.45) among all subscales. 

Nevertheless, the study also reveals areas where the design could be refined. The lower Dependability score suggests that there is a gap between the user's expected behavior and what the tool allows them to do.
During the study, some participants expected to be able to modify every value within the flow graph, but the system required them to navigate back to the worksheet and modify it there. This gap could be addressed by allowing the user to change these values with careful handling when it could destroy existing formulas. Similarly, the feedback in the custom questions about the expansion point visibility and the interaction-intensive task of expanding all reference nodes suggests the need for shortcuts or more efficient traversal of the flow graph in deeply nested formulas. The next design iteration could, for example, introduce a collapse all or an expand all button.

Finally, all participants, regardless of prior spreadsheet knowledge, were able to complete the comprehension and manipulation tasks, which provides initial evidence for the tool's accessibility. Furthermore, the mean perspicuity importance rating of 6.40, which was the highest among all importance subscales, underscores that ease of learning is very important to users. For future iterations, it should be a design priority to maintain or even improve the learnability of the system, especially for users who may not understand function arguments or lookup semantics.
