\section{Qualitative Results}
\subsection{Positive feedback}
After the NASA-TLX and UEQ+ questionnaire the participants were invited to fill out the three open-ended questions. For the first question: "What did you like the most about the tool?", the most mentioned strength was that the tool helped the user to understand the logic behind cells. Participant 1 writes:"it helped me understand the hidden meaning of the numbers of the sheet". Which aligns with the tool's goal.

Another major theme was the navigation and flow graph. This corresponds a lot with the Intuitive Use scale of the UEQ+ questionnaire, which achieved a median of 5.80. Participant 5 mentions that:"The flow chart made it very easy to understand the logic behind each cell. Especially the navigation by double-clicking was very intuitive."

\subsection{Frustrations}
All the participants had different frustrations. One theme which was mentioned by two particpants was that opening all the expandable reference nodes could be irritating. Participant 4 writes: "in a long tree, sometimes difficult to understand interdependacies". But Participant 4 is not sure if this is caused by the tool or by the nature of the more compex formulas.
Another concern of Participant 1 was the missing of a clear button. Participant 1 wished to return to a clean state after deep exploration. The Participant with lowest spreadsheet knowledge, Participant 3, mentions that the arguments of functions were a bit frustrating and that they felt a bit like blackboxes.
% TODO: write something that acknowledges this and that the tools theoretically should exactly solve this but maybe it solved that the functions are no longer blackboxes but now the arguments are blackboxes

\subsection{Improvement Suggestions}
The participants offered different improvement suggestions. Based on the frustration of Participant 1, Participant 1 would add a clean button in order to get a clean state of the tool on demand. Participant 2 suggested making expansion points more visible and also highlight expansion points when "unclicked" and gray when clicked. This is the reverse behavior of the current implemented highlighting. Participant 2 also proposed to make the flow graph view and worksheet view adaptable. The users should be able to decide how much worksheet view or flow graph view they need. Participant 3 would improve the description of the question mark boxes and add more verbose description in order to explain in more detail what the function does. Participant 5 proposed that clicking on a VLOOKUP result should show the user where exactly the result was found.

