\section{Quantitative Results}
\subsection{NASA-TLX Results}
% TODO: position the table more near the bar graph
% TODO: add source for RAW-TLX
\input{chapters/Evaluation/figures/table-tlx-scores.tex}
\input{chapters/Evaluation/figures/raw-nasa-tlx.tex}
The NASA-TLX results across the three spreadsheet tasks indicate that the users experience a low to moderate cognitive load when using the tool. The overall Raw TLX, an unweighted variant of the NASA Task Load Index that averages the subscales without a pairwise importance weighting, was 27.7 (SD = 11.8) on a 0-100 scale. Table~\ref{tab:nasa-tlx-subscales-table} presents the scores for all NASA-TLX dimensions across the three spreadsheet tasks, while figure~\ref{fig:raw-tlx-scores} only presents the overall Raw TLX score of each task with their respective standard deviation. This result is encouraging, because it indicates that the tool did not put an excessive cognitive burden on the participants, even when asked relative complex spreadsheet tasks. Task 2 achieved the lowest mean score of 23.2 (SD = 15.3), while Task 1 and Task 3 both achieved the highest mean score of 30.0 (SD = 9.5 and 18.9 respectively). The frustration levels were comparatively low, with means of 20.0, 10.0 and 15.0. This could indicate that even when participants encountered difficulties, that the tool was able to help them make some progress in the comprehension and that the interactions with the flow graph were intuitive. 
Important to mention is, that between the individual participants there was substantial variability across all tasks. For example, participant 5 consistently reported very low cognitive load (overall means of 16.0, 5.0, 8.0) whereas participant 2 reported a significant higher load with overall means of 29.0, 47.0 and 51.0. One reason for this variability could be the difference in spreadsheet knowledge, but the small sample size does not allow for generalizability.
%The table \ref{tab:nasa-tlx-subscales-table} presents all the subscale means for each of the three tasks and overall. The figure \ref{fig:raw-tlx-scores} presents all the Raw TLX scores for the tasks and the overall Raw TLX score. The overall mean across all tasks is 27.7 (SD = 14.4). This indicates that the tool does not meaningfully overburden users when using it. Task 1 produced a mean Raw TLX score of 30.0 (SD = 9.5). In this task the Effort was the dominant subscale, with a mean score of 42.0. This can be explained that in this task, the user did not only had to understand but also correct a wrong VLOOKUP in the spreadsheet.
%Task 2 produced the lowest mean Raw TLX score of the three tasks with a mean of 23.2 (SD = 15.3). Interesting is the subscale of perceived performance which has a mean of 37.0 but a standard deviation of 37.5 with values ranging from 5.0 up to 85.0. Which indicates that the participants had substantially different experiences of how well they accomplished the task, possibly reflecting genuine differences in accuracy or self-assessment. 
% Possibly assess how well participants did in certain questions and compare it to their self assessment.
%Task 3 shared the same mean Raw TLX score as Task 1 but with a higher standard deviation of SD~=~18.9, possibly reflecting how multi-sheet spreadsheet have a stronger impact based on the individual. Interesting is that some Participants with low knowledge level like Participant 1 (Knowledge = 2) achieved a Raw TLX score of 12.0 while Participant 4 with a higher knowledge level (Knowledge = 6) achieved a substantial higher Raw TLX score of 39.0. The mean of the mental demand in Task 3 is 42.0 which is slightly higher than the one in Task 1 but not significantly higher. Which does not align with the assumption that multi-sheet spreadsheet have higher complexity than single sheet spreadsheets.
%Across all tasks, Frustration was consistently the lowest-rated subscale with a mean of 15.0 (SD = 9.8). This indicates a positive signal, that even when participants encountered difficulties, they did not report sustained emotional frustration. 
%\input{chapters/Evaluation/figures/subscales-nasa-tlx.tex}
\subsection{UEQ+ Results}
\input{chapters/Evaluation/figures/ueq-bar-graph-remapped.tex}
% TODO: add citation for the redfining to -3 to 3 scale
% TODO: add importance rating table
The UEQ+ scores indicate an overall positive user experience with the tool across different quality dimensions. Figure \ref{fig:ueq-bar-graph-2} presents the mean scores and standard deviations for each UEQ+ scale. All seven subscales received a positive mean score, ranging from 1.45 up to 1.95.
% TODO: mention paper which gives these scores a context
The subscores Efficiency and Visual Clarity achieving the highest scores, both with mean scores of 1.95 (SD = 0.84 and SD = 0.45 respectively). The goal of the tool was to improve the self-descriptiveness of Spreadsheets and the results suggest that the tool was perceived both as practical and goal-supportive. Especially the high usefulness score (M = 1.90) combined with its high importance rating (M = 6.20 out of 7) indicates that the participants found the tool useful and also be highly relevant for this type of tool. % suprise ???
This is outcome is encouraging, because it indicates that the tools is well received in the dimensions that matter the most to users.
The perspicuity scale (M = 1.75), which describes how easy it is to learn and understand a tool, received the highest importance rating among all scales (M = 6.40), indicating that participants value if the tool is easy to learn and understandable. The score itself is positive, but has a notable variabiltiy (SD = 0.79), with one participant rating the perspicuity of the tool substantially lower (0.50) than others. This participant also self reported the lowest spreadsheet knowledge level of 1 and noted in the custom-questions that function arguments sometimes felt like a "blackbox". This could indicate that the tool has a steeper learning curve for beginners than intermediates.
Dependability (M = 1.45) received the lowest mean score among all subscales, though it remained in the positive range. Dependability descirbes if the tool behaves predictably and meets user expectations. This lower score can be attributed to some observed instances during the study, in which participants tried to edit cell reference nodes values even though they are formulas and therefore read-only. This result's indicates that there exists a gulf of execution, where the user's intended action does not map directly onto the system's interaction. A more predictable interaction would be if the system allows for formula containing reference nodes, like non formula contianing reference nodes, the ability to directly manipulate the value, even if it destroys the formula. % TODO: cite the norman concept of gulf of execution
The aesthetic scale (M = 1.75) received the lowest importance rating (M = 4.60), suggesting that the participants cared more about if the tool helps in achieving their goal than how it looks. Nevertheless, the positive result indicates that the participants liked the aesthetics of the tool. Also the aesthetic scale has the highest variability of all subscales (SD = 0.90) which could reflect the individual preferences for visual design.



%Figure \ref{fig:ueq-bar-graph} presents the means scores and standard deviations for each of the seven UEQ+-scales, alongside the mean importance and standard deviations provided by participants. All seven scales score above the neutral midpoint of 4, indicating that participants perceived the tool in general as positive. Efficiency (M = 5.95, SD = 0.84) and Clarity (M = 5.95, SD = 0.45) tie as the highest-rated scales. Which indicates that the participants had the impression, that the tool was helpful to solve the tasks without unnecessary effort. Important to mention is that Clarity exhibited the smallest standard deviation indicating a consensus that the tool was well organized and visually coherent. This consistency across participants with different expertise levels is a meaningful endorsement of the tool's architecture. The lowest score achieved the Dependability (M = 5.45, SD = 0.54), though it remained above the midpoint of 4.0. The lower scores appears connected to concerns about predictability and system supportiveness raised by individual participants. Especially Participant 4 rated the predictability and supportiveness at 4.0 while Participant 5, who has a comparable spreadsheet knowledge, rated it 7.0 and 6.0. 
%When comparing the scale scores with their importance ratings, perspicuity, the scale capturing how understandable and learnable the tool is, received the highest importance rating of all scales (M = 6.40, SD = 0.55). This indicates that learnability is the quality the participants most care about in this tool. The tool delievered on this dimension according to the participant, because the score of Perspicuity is 5.75. Visual Aesthetics received the most polarised importance rating ranging (M = 4.60, SD = 1.82). For some participants the aesthetics were extremely important, indicated with a score of 7/7, and for other users it was almost irrelevant, indicated with a score of 3/7. This suggests that aesthetic refinement is not a priority for this tool.
%The importance ratings further reveal a hierarchy of user priorities. Usefulness and Perspicuity tied as the most important qualities (both M = 6.20 and M = 6.40 respectively). Structure and Visual Aesthetics received the lowest importance ratings (M = 5.20 and M = 4.60), suggesting that while these dimensions are pleasant, that it is more important if the tool can help them understand the spreadsheet.
